---
title: "FDI Determinants Model"
author: "Damian Żamojda 386905"
date: "1/04/2021"
output:
  html_document: 
    keep_md: yes
---
# Libraries

```{r message=FALSE, results='hide', warning=FALSE}
rm(list=ls())
library(tidyverse)
library(ggplot2)
library(ggExtra)
library(here)
library(plm)
library(lmtest)
library(Hmisc)
library(corrplot)
library(readr)
library(treemapify)
library(broom)
library(kableExtra)
library(hrbrthemes)

library(pvclust)
library(ggpubr)
library(factoextra)
library(viridis)
library(fpc)

library(SHAPforxgboost)
library(xgboost)
library(data.table)
library(caTools)
library(caret)
library(tseries)

library(sjPlot)
library(sjmisc)
library(corrplot) 
library(Hmisc)
```

# Data Overview and outlier reduction

```{r message=FALSE, echo=FALSE, results='hide', warning=FALSE}
Data <- read_csv(here("Processed_Data", "FDI_Dataset.csv"))
Data <- Data[,2:31]
Data$Status <- as.factor(Data$Status)
Data$Exe_respect_constitution_cat <- as.factor(Data$Exe_respect_constitution_cat)
Data$FDI <- Data$FDI/Data$GDP
Data$num <- rownames(Data)
#Responses: 
#1: Free.
#2: Partly Free. 
#3: Not Free.
table(Data$Year)
sapply(Data, function(x) sum(is.na(x)))
```

```{r message=FALSE, echo=FALSE, warning=FALSE}
set.seed(12345)
# Ward Hierarchical Clustering with Bootstrapped p values
Data_clust <- Data %>% select(c(GDP_growth, GDP_p_capita, Pop, Trade_op, FiskalStatus, Country, Year, FDI, Exe_respect_constitution, P_rights, Civil_liberties, RuleOfLaw,Party_institut_idx)) %>% na.omit(GDP_growth, GDP_p_capita, Pop, Trade_op,Party_institut_idx)

# log() values
Data_clust$GDP_p_capita <- log(Data_clust$GDP_p_capita)
Data_clust$Trade_op <- log(Data_clust$Trade_op)
Data_clust$Pop <- log(Data_clust$Pop)

#Scalling
Data_clust$GDP_growth_Scaled <- scale(Data_clust$GDP_growth)
Data_clust$GDP_p_capita_Scaled <- scale(Data_clust$GDP_p_capita)
Data_clust$Pop_Scaled <- scale(Data_clust$Pop)
Data_clust$Trade_op_Scaled <- scale(Data_clust$Trade_op)
Data_clust$Party_institut_idx_Scaled <- scale(Data_clust$Party_institut_idx)
```

```{r message=FALSE, echo=FALSE, warning=FALSE}
# No. of clusters
fviz_nbclust(Data_clust[,14:18], FUNcluster=kmeans, method = "silhouette") + theme_minimal()
fviz_nbclust(Data_clust[,14:18], FUNcluster=kmeans, method = "wss") + theme_minimal()
fviz_nbclust(Data_clust[,14:18], FUNcluster=kmeans, method = "gap_stat") + theme_minimal()

my_vector <- vector("numeric", 10L)
for(i in 2:10) {
  clusters1<-kmeans(Data_clust[,14:18], 3) 
  my_vector[i] <- round(calinhara(Data_clust[,14:18],clusters1$cluster),digits=2)
}
ggplot(data_frame(my_vector), aes(x=seq(1,10,1), y=my_vector)) +
  geom_line() +
  labs(title="Ptimal number of clusters", x="Number of clusters k", y = "Calinski-Harabasz Index") + 
  geom_vline(xintercept = 3, linetype="dotted", color = "blue") + 
  scale_x_discrete(limits=seq(1,10,1)) +
  theme_minimal()  
```

```{r message=FALSE, echo=FALSE, warning=FALSE}
# Kmeans
clusters1<-kmeans(Data_clust[,14:18], 3)

# Plot
fviz_cluster(clusters1, Data_clust[,14:18])
```


```{r message=FALSE, echo=FALSE, warning=FALSE}
#Visualization
Data_clust %>%
  as_tibble() %>%
  mutate(cluster = clusters1$cluster) %>%
  ggplot(aes(GDP_growth, GDP_p_capita, color = factor(cluster), shape = factor(FiskalStatus))) +
  geom_point()

Data_clust %>%
  as_tibble() %>%
  mutate(cluster = clusters1$cluster) -> Data_clust

Data_clust %>%
  group_by(FiskalStatus, cluster) %>%
  summarise(n = n()) -> Data.agg.clust

ggplot(Data.agg.clust, aes(x = FiskalStatus, y = cluster)) +
  geom_tile(aes(fill = n), color = 'white', show.legend = F) +
  theme_minimal() + 
  geom_text(aes(label = n), size = 5, fontface = 'bold', color = 'white') +
  labs(title = 'Table 1. Country Status Distribution') +
  theme(panel.grid = element_blank())
```

```{r message=FALSE, echo=FALSE, warning=FALSE}
Data_clust %>% group_by(FiskalStatus) %>%
  select(FDI, Year) %>%
  summarise(Min = round(min(FDI),2),
            '1st Qu.' = round(quantile(FDI, 0.25),2),
            Median = round(median(FDI),2),
            Mean = round(mean(FDI),2),
            '3rd Qu.' = round(quantile(FDI, 0.75),2),
            Max = round(max(FDI),2),
            Std = round(sd(FDI),2),
            Count = n(),
            'Years (Min-Max)'= paste0(as.character(min(Year)), "-",as.character(max(Year)))) -> FDI_stats
FDI_stats %>% kable() %>% kable_styling()%>%
  save_kable("tables/table1.html",
             zoom = 2)

Data_clust %>% group_by(cluster) %>%
  select(FDI, Year) %>%
  summarise(Min = round(min(FDI),2),
            '1st Qu.' = round(quantile(FDI, 0.25),2),
            Median = round(median(FDI),2),
            Mean = round(mean(FDI),2),
            '3rd Qu.' = round(quantile(FDI, 0.75),2),
            Max = round(max(FDI),2),
            Std = round(sd(FDI),2),
            Count = n(),
            'Years (Min-Max)'= paste0(as.character(min(Year)), "-",as.character(max(Year)))) -> FDI_stats
FDI_stats %>% kable() %>% kable_styling()%>%
  save_kable("tables/table2.html",
             zoom = 2)
```

# After outlier analysis and removal

```{r message=FALSE, echo=FALSE, results='hide', warning=FALSE}
# 51 UFO Outliers
Data <- filter(Data_clust, (FiskalStatus == "Advanced" & cluster == 1) == FALSE)
Data <- Data[,c(1:13,19)]
colnames(Data) <- c("GDP_growth", "GDP_p_capita_log", "Pop_log", "Trade_op_log", "FiskalStatus", "Country", "Year", "FDI", "Exe_respect_constitution", "P_rights", "Civil_liberties", "RuleOfLaw", "Party_institut_idx", "cluster")
Data$num <- rownames(Data)

#Visualization
Data %>%
  group_by(FiskalStatus, cluster) %>%
  summarise(n = n()) -> Data.agg.clust

ggplot(Data.agg.clust, aes(x = FiskalStatus, y = cluster)) +
  geom_tile(aes(fill = n), color = 'white', show.legend = F) +
  theme_minimal() + 
  geom_text(aes(label = n), size = 5, fontface = 'bold', color = 'white') +
  theme(panel.grid = element_blank())
```

```{r message=FALSE, echo=FALSE, warning=FALSE}
Data %>% group_by(FiskalStatus) %>%
  select(FDI, Year) %>%
  summarise(Min = round(min(FDI),2),
            '1st Qu.' = round(quantile(FDI, 0.25),2),
            Median = round(median(FDI),2),
            Mean = round(mean(FDI),2),
            '3rd Qu.' = round(quantile(FDI, 0.75),2),
            Max = round(max(FDI),2),
            Std = round(sd(FDI),2),
            Count = n(),
            'Years (Min-Max)'= paste0(as.character(min(Year)), "-",as.character(max(Year)))) -> FDI_stats
FDI_stats %>% kable() %>% kable_styling()%>%
  save_kable("tables/table3.html",
             zoom = 2)

Data %>% group_by(cluster) %>%
  select(FDI, Year) %>%
  summarise(Min = round(min(FDI),2),
            '1st Qu.' = round(quantile(FDI, 0.25),2),
            Median = round(median(FDI),2),
            Mean = round(mean(FDI),2),
            '3rd Qu.' = round(quantile(FDI, 0.75),2),
            Max = round(max(FDI),2),
            Std = round(sd(FDI),2),
            Count = n(),
            'Years (Min-Max)'= paste0(as.character(min(Year)), "-",as.character(max(Year)))) -> FDI_stats
FDI_stats %>% kable() %>% kable_styling()%>%
  save_kable("tables/table4.html",
             zoom = 2)
```


# Sampling

```{r message=FALSE, echo=FALSE, results='hide', warning=FALSE}
unique(Data$Country)
unique(Data$Year)
# Advanced
Advanced_data <- filter(Data, FiskalStatus == "Advanced")
# Emerging
Emerging_data <- filter(Data, FiskalStatus == "Emerging")
# Low-Income
LowIncome_data <- filter(Data, FiskalStatus == "Low-income")
```

```{r message=FALSE, echo=FALSE, warning=FALSE}
Data$Fiscal_Status <- Data$FiskalStatus
Data %>% group_by(Fiscal_Status, Year) %>%
  summarise(FDI = mean(FDI)) %>%
  ggplot(aes(x= Year, y= FDI, color=Fiscal_Status)) +
  geom_line() +
  labs(y = 'FDI/GDP') +
  theme_minimal()

Data %>% group_by(Fiscal_Status, Year) %>%
  summarise(Exe_respect_constitution = mean(Exe_respect_constitution)) %>%
  ggplot(aes(x= Year, y= Exe_respect_constitution, color=Fiscal_Status)) +
  geom_line() +
  labs(y = 'Executives respects constitution') +
  theme_minimal()

Data %>% group_by(Fiscal_Status, Year) %>%
  summarise(Party_institut_idx = mean(Party_institut_idx)) %>%
  ggplot(aes(x= Year, y= Party_institut_idx, color=Fiscal_Status)) +
  geom_line() +
  labs(y = 'Party institutionalisation index') +
  theme_minimal()

Data %>% group_by(FiskalStatus, Year) %>%
  summarise(Trade_op_log = mean(Trade_op_log)) %>%
  ggplot(aes(x= Year, y= Trade_op_log, color=FiskalStatus)) +
  geom_line() +
  labs(y = 'Trade Openness') +
  theme_minimal()

Data %>% group_by(FiskalStatus, Year) %>%
  summarise(RuleOfLaw = mean(RuleOfLaw)) %>%
  ggplot(aes(x= Year, y= RuleOfLaw, color=FiskalStatus)) +
  geom_line() +
  labs(y = 'Rule Of Law') +
  theme_minimal()

Data %>% group_by(FiskalStatus, Year) %>%
  summarise(Civil_liberties = mean(Civil_liberties)) %>%
  ggplot(aes(x= Year, y= Civil_liberties, color=FiskalStatus)) +
  geom_line() +
  labs(y = 'Civil_liberties') +
  theme_minimal()
```

# Advanced Countries

```{r message=FALSE, echo=FALSE, warning=FALSE}
variables <- c("GDP_growth", "GDP_p_capita_log", "Pop_log", "P_rights", "Trade_op_log", "FDI", "Exe_respect_constitution", "Civil_liberties", "RuleOfLaw", "Year", "Party_institut_idx")
Advanced_data %>% select(variables, Country) %>% drop_na() %>% data.frame() -> stat_data
stat_data$FDI <- stat_data$FDI
stat_data %>% group_by(Country) %>%
  select(FDI, Year) %>%
  summarise(Min = round(min(FDI),2),
            '1st Qu.' = round(quantile(FDI, 0.25),2),
            Median = round(median(FDI),2),
            Mean = round(mean(FDI),2),
            '3rd Qu.' = round(quantile(FDI, 0.75),2),
            Max = round(max(FDI),2),
            Std = round(sd(FDI),2),
            Count = n(),
            'Years (Min-Max)'= paste0(as.character(min(Year)), "-",as.character(max(Year)))) -> FDI_stats



FDI_stats %>% kable() %>% kable_styling()%>%
  save_kable("tables/table5.html",
             zoom = 2)

```

```{r message=FALSE, echo=FALSE, warning=FALSE}
FDI_stats %>%
  mutate(Country = reorder(Country, Max)) %>%
  ggplot() +
  geom_segment( aes(x=Country, xend=Country, y=Min, yend=Max), color="grey") +
  geom_point( aes(x=Country, y=Min), color=rgb(0.2,0.7,0.1,0.5), size=3 ) +
  geom_point( aes(x=Country, y=Max), color=rgb(0.7,0.2,0.1,0.5), size=3 ) +
  coord_flip()+
  theme_ipsum() +
  theme(
    legend.position = "none",
  ) +
  xlab("") +
  ylab("Share of FDI in GDP")+
  scale_y_continuous(breaks=c(seq(0, 3,0.5)))+
  theme_minimal()
```


```{r message=FALSE, echo=FALSE, warning=FALSE}
data_corr <- Advanced_data %>% select(variables) %>% select(-Year) %>% drop_na()
nums <- unlist(lapply(data_corr, is.numeric)) 

col <- colorRampPalette(c("#BB4444", "#EE9988", "#FFFFFF", "#77AADD", "#4477AA"))
cor.mtest <- function(mat) {
    mat <- as.matrix(mat)
    n <- ncol(mat)
    p.mat<- matrix(NA, n, n)
    diag(p.mat) <- 0
    for (i in 1:(n - 1)) {
        for (j in (i + 1):n) {
            tmp <- cor.test(mat[, i], mat[, j])
            p.mat[i, j] <- p.mat[j, i] <- tmp$p.value
        }
    }
  colnames(p.mat) <- rownames(p.mat) <- colnames(mat)
  p.mat
}
```

```{r message=FALSE, echo=FALSE, warning=FALSE}
M <- data_corr[, nums]
colnames(M) <- c("GDP growth rate", "log(GDP per capita)","log(Population)","Property rights","log(Trade openness)","FDI", "Executive respects constitution","Civil Liberties","Rule of Law","Party institutionalization index")
res <- cor(M)
p.mat <- cor.mtest(M)

png('corr_plot1.png', width = 880, height = 880)

corrplot(res, is.corr = FALSE, method="color", col=col(200),
         type="upper", 
         addCoef.col = "black", # Add coefficient of correlation
         tl.col="black", tl.srt=45, #Text label color and rotation
         # Combine with significance
         p.mat = p.mat, sig.level = c(0.01), insig = 'blank', 
         # hide correlation coefficient on the principal diagonal
         diag=FALSE 
         )

dev.off()
```

## Panel Model

### Exe_respect_constitution Clustering

```{r message=FALSE, echo=FALSE, warning=FALSE}
set.seed(1234567890)
Data_Advanced_clust <- Advanced_data %>% select(c(Exe_respect_constitution)) %>% scale()

fviz_nbclust(Data_Advanced_clust, FUNcluster=kmeans, method = "silhouette") + theme_minimal()
fviz_nbclust(Data_Advanced_clust, FUNcluster=kmeans, method = "wss") + theme_minimal()
fviz_nbclust(Data_Advanced_clust, FUNcluster=kmeans, method = "gap_stat") + theme_minimal()

my_vector <- vector("numeric", 10L)
for(i in 2:10) {
  clusters1<-kmeans(Data_Advanced_clust, 3) 
  my_vector[i] <- round(calinhara(Data_Advanced_clust,clusters1$cluster),digits=2)
}
ggplot(data_frame(my_vector), aes(x=seq(1,10,1), y=my_vector)) +
  geom_line() +
  labs(title="Optimal number of clusters",
       x="Number of clusters k", y = "Calinski-Harabasz Index") + 
  geom_vline(xintercept = 3, linetype="dotted", color = "blue") + 
  scale_x_discrete(limits=seq(1,10,1)) +
  theme_minimal()  

clusters1<-kmeans(Data_Advanced_clust, 3) # 3 clusters final

Advanced_data$Exe_clust<-rep(0, times=dim(Advanced_data)[1])
Advanced_data$Exe_clust[clusters1$cluster==1]<-1
Advanced_data$Exe_clust[clusters1$cluster==2]<-2
Advanced_data$Exe_clust[clusters1$cluster==3]<-3

clusters_stats <- cbind(Advanced_data$Exe_respect_constitution[clusters1$cluster==1],
                        Advanced_data$Exe_respect_constitution[clusters1$cluster==2],
                        Advanced_data$Exe_respect_constitution[clusters1$cluster==3])
colnames(clusters_stats) <- c("Cluster 1", "Cluster 2", "Cluster 3")
summary(clusters_stats)
Advanced_data$Exe_clust <- ordered(Advanced_data$Exe_clust, c("1","2", "3"))

plot_cluster <- cbind(Advanced_data$Exe_respect_constitution, clusters1$cluster)
colnames(plot_cluster) <- c("Exe_respect_constitution", "Cluster")

ggplot(as.data.frame(plot_cluster),  aes(Exe_respect_constitution, Cluster, color=factor(Cluster))) +
  geom_point() +
  labs(title="Clusters Plot - Advanced Countries",
       x="Exe_respect_constitution", y = "Cluster's No.") +
  scale_y_discrete(limits=seq(1,3,1)) +
  theme_minimal() +
  theme(legend.position = "none")
table(Advanced_data$Exe_clust)
```

```{r message=FALSE, echo=FALSE, warning=FALSE}
as.data.frame(Advanced_data) %>% mutate(Cluster = Exe_clust) %>%
  group_by(Cluster) %>%
  summarise(Min = round(min(Exe_respect_constitution),4),
            '1st Qu.' = round(quantile(Exe_respect_constitution, 0.25),4),
            Median = round(median(Exe_respect_constitution),4),
            Mean = round(mean(Exe_respect_constitution),4),
            '3rd Qu.' = round(quantile(Exe_respect_constitution, 0.75),4),
            Max = round(max(Exe_respect_constitution),4),
            Std = round(sd(Exe_respect_constitution),4),
            Count = n()) -> Exe_stats
Exe_stats %>% kable() %>% kable_styling()%>%
  save_kable("tables/table1exe.html",
             zoom = 2)
```
### model 1

```{r message=FALSE, echo=FALSE, warning=FALSE}
formula <- log(FDI) ~ GDP_growth + GDP_p_capita_log + Pop_log + Trade_op_log + Party_institut_idx + P_rights

fixed <- plm(formula, data = Advanced_data, index = c("Country", "Year"), model = "within")
random <- plm(formula, data = Advanced_data, index = c("Country", "Year"), model = "random")
pooled <- plm(formula, data = Advanced_data, index = c("Country", "Year"), model = "pooling")

x <- phtest(fixed,random)
x <- x[["p.value"]]

if (x>=0.05) {
  Advanced_model1 <- random} else{
    Advanced_model1 <- fixed
  }# if pvalue <= 0,05 : H0:random is ejected - we use fixed effects (Hausman 1978)

summary(Advanced_model1)

# Fixed effects test
Test_table1_Advanced <- tidy(pFtest(fixed, pooled))
# Hausman Test
Test_table2_Advanced <- tidy(phtest(fixed,random))

rm(random, fixed, x, pooled)  
```

### model 2

```{r message=FALSE, echo=FALSE, warning=FALSE}
formula <- log(FDI) ~ GDP_growth + GDP_p_capita_log + Pop_log + Trade_op_log + Party_institut_idx + Exe_clust

fixed <- plm(formula, data = Advanced_data, index = c("Country", "Year"), model = "within")
random <- plm(formula, data = Advanced_data, index = c("Country", "Year"), model = "random")
pooled <- plm(formula, data = Advanced_data, index = c("Country", "Year"), model = "pooling")

x <- phtest(fixed,random)
x <- x[["p.value"]]

if (x>=0.05) {
  Advanced_model2 <- random} else{
    Advanced_model2 <- fixed
  }# if pvalue <= 0,05 : H0:random is ejected - we use fixed effects (Hausman 1978)
summary(Advanced_model2)

# Fixed effects test
Test_table1_Advanced <- rbind(Test_table1_Advanced, tidy(pFtest(fixed, pooled)))
# Hausman Test
Test_table2_Advanced <- rbind(Test_table2_Advanced, tidy(phtest(fixed,random)))

rm(random, fixed, x, pooled)
```

### model 3

```{r message=FALSE, echo=FALSE, warning=FALSE}
formula <- log(FDI) ~ GDP_growth + GDP_p_capita_log + Pop_log + Trade_op_log + Party_institut_idx + RuleOfLaw

fixed <- plm(formula, data = Advanced_data, index = c("Country", "Year"), model = "within")
random <- plm(formula, data = Advanced_data, index = c("Country", "Year"), model = "random")
pooled <- plm(formula, data = Advanced_data, index = c("Country", "Year"), model = "pooling")

x <- phtest(fixed,random)
x <- x[["p.value"]]

if (x>=0.05) {
  Advanced_model3 <- random} else{
    Advanced_model3 <- fixed
  }# if pvalue <= 0,05 : H0:random is ejected - we use fixed effects (Hausman 1978)

summary(Advanced_model3)

# Fixed effects test
Test_table1_Advanced <- rbind(Test_table1_Advanced, tidy(pFtest(fixed, pooled)))
# Hausman Test
Test_table2_Advanced <- rbind(Test_table2_Advanced, tidy(phtest(fixed,random)))

rm(random, fixed, x, pooled)
```

### model 4

```{r message=FALSE, echo=FALSE, warning=FALSE}
formula <- log(FDI) ~ GDP_growth + GDP_p_capita_log + Pop_log + Trade_op_log + Party_institut_idx + Civil_liberties

fixed <- plm(formula, data = Advanced_data, index = c("Country", "Year"), model = "within")
random <- plm(formula, data = Advanced_data, index = c("Country", "Year"), model = "random")
pooled <- plm(formula, data = Advanced_data, index = c("Country", "Year"), model = "pooling")

x <- phtest(fixed,random)
x <- x[["p.value"]]

if (x>=0.05) {
  Advanced_model4 <- random} else{
    Advanced_model4 <- fixed
  }# if pvalue <= 0,05 : H0:random is ejected - we use fixed effects (Hausman 1978)
summary(Advanced_model4)

# Fixed effects test
Test_table1_Advanced <- rbind(Test_table1_Advanced, tidy(pFtest(fixed, pooled)))
# Hausman Test
Test_table2_Advanced <- rbind(Test_table2_Advanced, tidy(phtest(fixed,random)))

rm(random, fixed, x, pooled)
```


### model 5

```{r message=FALSE, echo=FALSE, warning=FALSE}
formula <- log(FDI) ~ lag(log(FDI)) + lag(log(FDI), 2) + GDP_growth + GDP_p_capita_log + Party_institut_idx + Pop_log + Trade_op_log

fixed <- plm(formula, data = Advanced_data, index = c("Country", "Year"), model = "within")
random <- plm(formula, data = Advanced_data, index = c("Country", "Year"), model = "random")
pooled <- plm(formula, data = Advanced_data, index = c("Country", "Year"), model = "pooling")

x <- phtest(fixed,random)
x <- x[["p.value"]]

if (x>=0.05) {
  Advanced_model5 <- random} else{
    Advanced_model5 <- fixed
  }# if pvalue <= 0,05 : H0:random is ejected - we use fixed effects (Hausman 1978)
summary(Advanced_model5)

# Fixed effects test
Test_table1_Advanced <- rbind(Test_table1_Advanced, tidy(pFtest(fixed, pooled)))
# Hausman Test
Test_table2_Advanced <- rbind(Test_table2_Advanced, tidy(phtest(fixed,random)))

rm(random, fixed, x, pooled)
```

### Panel Summary

```{r message=FALSE, echo=FALSE, warning=FALSE}
var_labels <- c(
  GDP_growth = "GDP growth rate",
  'GDP_p_capita_log' = "log(GDP per capita)",
  'Pop_log' = "log(Population)",
  'Trade_op_log' = "log(Trade openness)",
  P_rights = "Property rights", 
  Exe_clust = "Clustered Executive respects constitution",
  RuleOfLaw = "Rule of Law",
  Civil_liberties = "Civil Liberties",
  Party_institut_idx = "Party institutionalization index",
  Exe_clust.L = "Executive respects constitution .L",
  Exe_clust.Q = "Executive respects constitution .Q",
  'lag(log(FDI))' = "Lagged log(FDI) t-1",
  'lag(log(FDI), 2)' = "Lagged log(FDI) t-2"
)

tab_model(Advanced_model1, Advanced_model2, Advanced_model3, Advanced_model4, Advanced_model5,
          dv.labels = c("Model 1", "Model 2", "Model 3", "Model 4", "Model 5"),
          pred.labels = var_labels,
          show.ci = FALSE,
          p.style = "stars")
```

## XGBoost

### Sampling

```{r message=FALSE, echo=FALSE, warning=FALSE}
variables <- c("GDP_growth", "GDP_p_capita_log", "Pop_log", "P_rights", "Trade_op_log", "FDI", "Exe_respect_constitution", "Exe_clust", "Party_institut_idx")

sample = sample.split(Advanced_data$num, SplitRatio = .8)
Advanced_train = subset(Advanced_data, sample == TRUE)
Advanced_test  = subset(Advanced_data, sample == FALSE)
dim(Advanced_train)
dim(Advanced_test)
```

### Training 

Process starts with min_child_weight spectrum: c(10, 25, 50, 100, 150, 200, 500) and then respectively max_depth = seq(4,8,1); colsample_bytree = seq(0.1, 1, 0.1); subsample = c(0.6, 0.7, 0.75, 0.8, 0.85, 0.9); nrounds = seq(10,80,10).

### Model

```{r message=FALSE, echo=FALSE, results='hide', warning=FALSE}
set.seed(123456789)

y_var <-  "FDI"
dataX <- as.matrix(cbind(Advanced_train[,c(1:4,13)], as.numeric(Advanced_train$Exe_clust)))
colnames(dataX) <- c("GDP_growth","GDP_p_capita_log","Pop_log", "Trade_op_log","Party_institut_idx","Exe_clust")

param_list <- list(objective = "reg:squarederror",  # For regression
                   eta = 0.05,
                   max_depth = 6,
                   gamma = 0,
                   colsample_bytree = 0.8,
                   min_child_weight = 10,
                   subsample = 0.6
                   )

mod <- xgboost::xgboost(data = dataX, 
                        label = as.matrix(Advanced_train[[y_var]]), 
                        params = param_list, nrounds = 2)
xgb.dump(mod)
```

```{r message=FALSE, echo=FALSE, results='hide', warning=FALSE}
shap_values <- shap.values(xgb_model = mod, X_train = dataX)
shap_values$mean_shap_score %>% kable() %>% kable_styling()%>%
  save_kable("tables/table6.html",
             zoom = 2)
```

```{r message=FALSE, echo=FALSE, results='hide', warning=FALSE}
shap_data <- copy(shap_values$shap_score)
shap_data[, BIAS := shap_values$BIAS0]
pred_mod <- predict(mod, dataX, ntreelimit = 10)
shap_data[, `:=`(rowSum = round(rowSums(shap_data),6), pred_mod = round(pred_mod,6))]
```

```{r message=FALSE, echo=FALSE, results='hide', warning=FALSE}
# To prepare the long-format data:
shap_long <- shap.prep(shap_contrib = shap_values$shap_score, X_train = dataX)

# **SHAP summary plot**
shap.plot.summary(shap_long, scientific = FALSE)

plot_shap <- cbind(Advanced_data$Party_institut_idx, shap_values$shap_score$Party_institut_idx)
colnames(plot_shap) <- c("Party_institut_idx", "Shap_score")
ggplot(as.data.frame(plot_shap),  aes(Party_institut_idx, Shap_score, color=Party_institut_idx)) +
  geom_point() +
  geom_smooth() +
  labs(title="SHAP Plot - Advanced Countries",
       x="Party_institut_idx", y = "Shap_score") +
  theme_minimal()

plot_shap <- cbind(Advanced_data$Exe_clust,
                   shap_values$shap_score$Exe_clust)
colnames(plot_shap) <- c("Exe_clust", "Shap_score")
```

```{r message=FALSE, echo=FALSE, results='hide', warning=FALSE}
plot_shap <- cbind(Advanced_data$Exe_clust,
                   shap_values$shap_score$Exe_clust,
                   Advanced_data$Exe_respect_constitution)
colnames(plot_shap) <- c("Exe_clust", "Shap_score", "Exe_respect_constitution")

ggplot(as.data.frame(plot_shap),  aes(Exe_respect_constitution, Shap_score, color=Exe_respect_constitution, shape=ordered(Exe_clust, c("3","2", "1")))) +
  geom_point() +
  geom_smooth() +
  labs(title="SHAP Plot - Advanced Countries",
       x="Exe_clust", y = "Shap_score") +
  theme_minimal() -> p
p3 <- ggMarginal(p, type="boxplot")
p3 
```


```{r message=FALSE, echo=FALSE, results='hide', warning=FALSE}
# choose to show top 4 features by setting `top_n = 6`, 
# set 4 clustering groups of observations.  
plot_data <- shap.prep.stack.data(shap_contrib = shap_values$shap_score, top_n = 6, n_groups = 4)
# you may choose to zoom in at a location, and set y-axis limit using `y_parent_limit`  
shap.plot.force_plot(plot_data, zoom_in_location = 300)
```

```{r message=FALSE, echo=FALSE, results='hide', warning=FALSE}
shap.plot.force_plot_bygroup(plot_data)
```

# Emerging Countries

```{r message=FALSE, echo=FALSE, warning=FALSE}
variables <- c("GDP_growth", "GDP_p_capita_log", "Pop_log", "P_rights", "Trade_op_log", "FDI", "Exe_respect_constitution", "Civil_liberties", "RuleOfLaw", "Year", "Party_institut_idx")
stat_data <- Emerging_data %>% select(variables, Country) %>% drop_na() %>% data.frame()
stat_data$FDI <- stat_data$FDI
stat_data %>% group_by(Country) %>%
  select(FDI, Year) %>%
  summarise(Min = round(min(FDI),2),
            '1st Qu.' = round(quantile(FDI, 0.25),2),
            Median = round(median(FDI),2),
            Mean = round(mean(FDI),2),
            '3rd Qu.' = round(quantile(FDI, 0.75),2),
            Max = round(max(FDI),2),
            Std = round(sd(FDI),2),
            Count = n(),
            'Years (Min-Max)'= paste0(as.character(min(Year)), "-",as.character(max(Year)))) -> FDI_stats
FDI_stats %>% kable() %>% kable_styling()%>%
  save_kable("tables/table7.html",
             zoom = 2)
```

```{r message=FALSE, echo=FALSE, warning=FALSE}
FDI_stats %>%
  mutate(Country = reorder(Country, Max)) %>%
  ggplot() +
  geom_segment( aes(x=Country, xend=Country, y=Min, yend=Max), color="grey") +
  geom_point( aes(x=Country, y=Min), color=rgb(0.2,0.7,0.1,0.5), size=3 ) +
  geom_point( aes(x=Country, y=Max), color=rgb(0.7,0.2,0.1,0.5), size=3 ) +
  coord_flip()+
  theme_ipsum() +
  theme(
    legend.position = "none",
  ) +
  xlab("") +
  ylab("Share of FDI in GDP")+
  scale_y_continuous(breaks=c(seq(0, 4.5,0.5)))+
  theme_minimal()
```

```{r message=FALSE, echo=FALSE, warning=FALSE}
data_corr <- Emerging_data %>% select(variables) %>% select(-Year) %>% drop_na()
nums <- unlist(lapply(data_corr, is.numeric))  
```
```{r message=FALSE, echo=FALSE, warning=FALSE}
M <- data_corr[, nums]
colnames(M) <- c("GDP growth rate", "log(GDP per capita)","log(Population)","Property rights","log(Trade openness)","FDI", "Executive respects constitution","Civil Liberties","Rule of Law","Party institutionalization index")
res <- cor(M)
p.mat <- cor.mtest(M)


png('corr_plot2.png', width = 880, height = 880)

corrplot(res, is.corr = FALSE, method="color", col=col(200),
         type="upper", 
         addCoef.col = "black", # Add coefficient of correlation
         tl.col="black", tl.srt=45, #Text label color and rotation
         # Combine with significance
         p.mat = p.mat, sig.level = c(0.01), insig = 'blank', 
         # hide correlation coefficient on the principal diagonal
         diag=FALSE 
         )

dev.off()
```

## Panel Model

### Exe_respect_constitution Clustering

```{r message=FALSE, echo=FALSE, warning=FALSE}
Data_Emerging_clust <- Emerging_data %>% select(c(Exe_respect_constitution)) %>% scale()

fviz_nbclust(Data_Emerging_clust, FUNcluster=kmeans, method = "silhouette") + theme_minimal()
fviz_nbclust(Data_Emerging_clust, FUNcluster=kmeans, method = "wss") + theme_minimal()
fviz_nbclust(Data_Emerging_clust, FUNcluster=kmeans, method = "gap_stat") + theme_minimal()

my_vector <- vector("numeric", 10L)
for(i in 2:10) {
  clusters1<-kmeans(Data_Emerging_clust, 3) 
  my_vector[i] <- round(calinhara(Data_Emerging_clust,clusters1$cluster),digits=2)
}
ggplot(data_frame(my_vector), aes(x=seq(1,10,1), y=my_vector)) +
  geom_line() +
  labs(title="Optimal number of clusters",
       x="Number of clusters k", y = "Calinski-Harabasz Index") + 
  geom_vline(xintercept = 3, linetype="dotted", color = "blue") + 
  scale_x_discrete(limits=seq(1,10,1)) +
  theme_minimal()  

clusters1<-kmeans(Data_Emerging_clust, 3) # 3 clusters final

Emerging_data$Exe_clust<-rep(0, times=dim(Emerging_data)[1])
Emerging_data$Exe_clust[clusters1$cluster==1]<-1
Emerging_data$Exe_clust[clusters1$cluster==2]<-2
Emerging_data$Exe_clust[clusters1$cluster==3]<-3

clusters_stats <- cbind(Emerging_data$Exe_respect_constitution[clusters1$cluster==1],
                        Emerging_data$Exe_respect_constitution[clusters1$cluster==2],
                        Emerging_data$Exe_respect_constitution[clusters1$cluster==3])
colnames(clusters_stats) <- c("Cluster 1", "Cluster 2", "Cluster 3")
summary(clusters_stats)
Emerging_data$Exe_clust <- ordered(Emerging_data$Exe_clust, c("1","2", "3"))

plot_cluster <- cbind(Emerging_data$Exe_respect_constitution, clusters1$cluster)
colnames(plot_cluster) <- c("Exe_respect_constitution", "Cluster")

ggplot(as.data.frame(plot_cluster),  aes(Exe_respect_constitution, Cluster, color=factor(Cluster))) +
  geom_point() +
  labs(title="Clusters Plot - Emerging Countries",
       x="Exe_respect_constitution", y = "Cluster's No.") +
  scale_y_discrete(limits=seq(1,3,1)) +
  theme_minimal() +
  theme(legend.position = "none")
table(Emerging_data$Exe_clust)
```

```{r message=FALSE, echo=FALSE, warning=FALSE}
as.data.frame(Emerging_data) %>% mutate(Cluster = Exe_clust) %>%
  group_by(Cluster) %>%
  summarise(Min = round(min(Exe_respect_constitution),4),
            '1st Qu.' = round(quantile(Exe_respect_constitution, 0.25),4),
            Median = round(median(Exe_respect_constitution),4),
            Mean = round(mean(Exe_respect_constitution),4),
            '3rd Qu.' = round(quantile(Exe_respect_constitution, 0.75),4),
            Max = round(max(Exe_respect_constitution),4),
            Std = round(sd(Exe_respect_constitution),4),
            Count = n()) -> Exe_stats
Exe_stats %>% kable() %>% kable_styling()%>%
  save_kable("tables/table2exe.html",
             zoom = 2)
```

### model 1

```{r message=FALSE, echo=FALSE, warning=FALSE}
formula <- log(FDI) ~ GDP_growth + GDP_p_capita_log + Pop_log + Trade_op_log + Party_institut_idx + P_rights

fixed <- plm(formula, data = Emerging_data, index = c("Country", "Year"), model = "within")
random <- plm(formula, data = Emerging_data, index = c("Country", "Year"), model = "random")
pooled <- plm(formula, data = Emerging_data, index = c("Country", "Year"), model = "pooling")

# Exception - we decide to use fixed model
Emerging_model1 <- fixed
summary(Emerging_model1)

# Fixed effects test
Test_table1_Emerging <- tidy(pFtest(fixed, pooled))
# Hausman Test
Test_table2_Emerging <- tidy(phtest(fixed,random))

rm(random, fixed, x, pooled)    
```

### model 2

```{r message=FALSE, echo=FALSE, warning=FALSE}
formula <- log(FDI) ~ GDP_growth + GDP_p_capita_log + Pop_log + Trade_op_log + Party_institut_idx + Exe_clust

fixed <- plm(formula, data = Emerging_data, index = c("Country", "Year"), model = "within")
random <- plm(formula, data = Emerging_data, index = c("Country", "Year"), model = "random")
pooled <- plm(formula, data = Emerging_data, index = c("Country", "Year"), model = "pooling")

# Exception - we decide to use fixed model
Emerging_model2 <- fixed
summary(Emerging_model2)

# Fixed effects test
Test_table1_Emerging <- rbind(Test_table1_Emerging, tidy(pFtest(fixed, pooled)))
# Hausman Test
Test_table2_Emerging <- rbind(Test_table2_Emerging, tidy(phtest(fixed,random)))

rm(random, fixed, x, pooled)

```

### model 3

```{r message=FALSE, echo=FALSE, warning=FALSE}
formula <- log(FDI) ~ GDP_growth + GDP_p_capita_log + Pop_log + Trade_op_log + Party_institut_idx + RuleOfLaw

fixed <- plm(formula, data = Emerging_data, index = c("Country", "Year"), model = "within")
random <- plm(formula, data = Emerging_data, index = c("Country", "Year"), model = "random")
pooled <- plm(formula, data = Emerging_data, index = c("Country", "Year"), model = "pooling")

# Exception - we decide to use fixed model
Emerging_model3 <- fixed
summary(Emerging_model3)

# Fixed effects test
Test_table1_Emerging <- rbind(Test_table1_Emerging, tidy(pFtest(fixed, pooled)))
# Hausman Test
Test_table2_Emerging <- rbind(Test_table2_Emerging, tidy(phtest(fixed,random)))

rm(random, fixed, x, pooled)
```

### model 4

```{r message=FALSE, echo=FALSE, warning=FALSE}
formula <- log(FDI) ~ GDP_growth + GDP_p_capita_log + Pop_log + Trade_op_log + Party_institut_idx + Civil_liberties

fixed <- plm(formula, data = Emerging_data, index = c("Country", "Year"), model = "within")
random <- plm(formula, data = Emerging_data, index = c("Country", "Year"), model = "random")
pooled <- plm(formula, data = Emerging_data, index = c("Country", "Year"), model = "pooling")

# Exception - we decide to use fixed model
Emerging_model4 <- fixed
summary(Emerging_model4)

# Fixed effects test
Test_table1_Emerging <- rbind(Test_table1_Emerging, tidy(pFtest(fixed, pooled)))
# Hausman Test
Test_table2_Emerging <- rbind(Test_table2_Emerging, tidy(phtest(fixed,random)))
rm(random, fixed, x, pooled)
```

### model 5

```{r message=FALSE, echo=FALSE, warning=FALSE}
formula <- log(FDI) ~ lag(log(FDI)) + lag(log(FDI), 2) + GDP_growth + GDP_p_capita_log + Pop_log + Trade_op_log + Party_institut_idx

fixed <- plm(formula, data = Emerging_data, index = c("Country", "Year"), model = "within")
random <- plm(formula, data = Emerging_data, index = c("Country", "Year"), model = "random")
pooled <- plm(formula, data = Emerging_data, index = c("Country", "Year"), model = "pooling")

x <- phtest(fixed,random)
x <- x[["p.value"]]

if (x>=0.05) {
  Emerging_model5 <- random} else{
    Emerging_model5 <- fixed
  }# if pvalue <= 0,05 : H0:random is ejected - we use fixed effects (Hausman 1978)
summary(Emerging_model5)

# Fixed effects test
Test_table1_Emerging <- rbind(Test_table1_Emerging, tidy(pFtest(fixed, pooled)))
# Hausman Test
Test_table2_Emerging <- rbind(Test_table2_Emerging, tidy(phtest(fixed,random)))

rm(random, fixed, x, pooled)
```

### Panel Summary

```{r message=FALSE, echo=FALSE, warning=FALSE}
tab_model(Emerging_model1, Emerging_model2, Emerging_model3, Emerging_model4, Emerging_model5,
          dv.labels = c("Model 1", "Model 2", "Model 3", "Model 4", "Model 5"),
          pred.labels = var_labels,
          show.ci = FALSE,
          p.style = "stars")
```

## XGBoost

### Sampling

```{r message=FALSE, echo=FALSE, warning=FALSE}
sample = sample.split(Emerging_data$num, SplitRatio = .8)
Emerging_train = subset(Emerging_data, sample == TRUE)
Emerging_test  = subset(Emerging_data, sample == FALSE)
dim(Emerging_train)
dim(Emerging_test)
```

### Training 

Process starts with min_child_weight spectrum: c(10, 25, 50, 100, 150, 200, 500, 1000) and then respectively max_depth = seq(4,8,1); colsample_bytree = seq(0.1, 1, 0.1); subsample = c(0.6, 0.7, 0.75, 0.8, 0.85, 0.9); nrounds = seq(10,80,10).

```{r message=FALSE, echo=FALSE, results='hide', warning=FALSE}
formula <- log(FDI) ~ GDP_growth + GDP_p_capita_log + Pop_log + Trade_op_log + P_rights + Civil_liberties

parameters_xgb <- expand.grid(nrounds = 50,
                             max_depth = 6,
                             eta = 0.25, 
                             gamma = 1,
                             colsample_bytree = 1,
                             min_child_weight = 10,
                             subsample = 0.75)
ctrl_cv3 <- trainControl(method = "cv", 
                         number = 3)

set.seed(123456789)
FDI.xgb <- caret::train(formula,
                     data = Emerging_train,
                     method = "xgbTree",
                     trControl = ctrl_cv3,
                     tuneGrid  = parameters_xgb,
                     tuneLength = 10)
FDI.xgb

```

### Model

```{r message=FALSE, warning=FALSE, results='hide'}
set.seed(123456789)

y_var <-  "FDI"
dataX <- as.matrix(cbind(Emerging_train[,c(1:4,13)], as.numeric(Emerging_train$Exe_clust)))
colnames(dataX) <- c("GDP_growth","GDP_p_capita_log","Pop_log", "Trade_op_log","Party_institut_idx","Exe_clust")

param_list <- list(objective = "reg:squarederror",  # For regression
                   eta = 0.05,
                   max_depth = 6,
                   gamma = 0,
                   colsample_bytree = 0.8,
                   min_child_weight = 10,
                   subsample = 0.6
                   )

mod <- xgboost::xgboost(data = dataX, 
                        label = as.matrix(Emerging_train[[y_var]]), 
                        params = param_list, nrounds = 100)
```


```{r message=FALSE, echo=FALSE, results='hide', warning=FALSE}
shap_values <- shap.values(xgb_model = mod, X_train = dataX)
shap_values$mean_shap_score
```

```{r message=FALSE, echo=FALSE, results='hide', warning=FALSE}
shap_data <- copy(shap_values$shap_score)
shap_data[, BIAS := shap_values$BIAS0]
pred_mod <- predict(mod, dataX, ntreelimit = 10)
shap_data[, `:=`(rowSum = round(rowSums(shap_data),6), pred_mod = round(pred_mod,6))]
```

```{r message=FALSE, echo=FALSE, results='hide', warning=FALSE}
# To prepare the long-format data:
shap_long <- shap.prep(xgb_model = mod, X_train = dataX)

# **SHAP summary plot**
shap.plot.summary(shap_long)

plot_shap <- cbind(Emerging_data$Party_institut_idx, shap_values$shap_score$Party_institut_idx)
colnames(plot_shap) <- c("Party_institut_idx", "Shap_score")
ggplot(as.data.frame(plot_shap),  aes(Party_institut_idx, Shap_score, color=Party_institut_idx)) +
  geom_point() +
  geom_smooth() +
  labs(title="SHAP Plot - Emerging Countries",
       x="Party_institut_idx", y = "Shap_score") +
  theme_minimal()

plot_shap <- cbind(Emerging_data$Exe_clust,
                   shap_values$shap_score$Exe_clust)
colnames(plot_shap) <- c("Exe_clust", "Shap_score")
```

```{r message=FALSE, echo=FALSE, results='hide', warning=FALSE}
plot_shap <- cbind(Emerging_data$Exe_clust,
                   shap_values$shap_score$Exe_clust,
                   Emerging_data$Exe_respect_constitution)
colnames(plot_shap) <- c("Exe_clust", "Shap_score", "Exe_respect_constitution")

ggplot(as.data.frame(plot_shap),  aes(Exe_respect_constitution, Shap_score, color=Exe_respect_constitution, shape=ordered(Exe_clust, c("3","2", "1")))) +
  geom_point() +
  geom_smooth() +
  labs(title="SHAP Plot - Emerging Countries",
       x="Exe_clust", y = "Shap_score") +
  theme_minimal() -> p
p3 <- ggMarginal(p, type="boxplot")
p3 
```



```{r message=FALSE, echo=FALSE, results='hide', warning=FALSE}
# choose to show top 4 features by setting `top_n = 6`, 
# set 4 clustering groups of observations.  
plot_data <- shap.prep.stack.data(shap_contrib = shap_values$shap_score, top_n = 6, n_groups = 4)
# you may choose to zoom in at a location, and set y-axis limit using `y_parent_limit`  
shap.plot.force_plot(plot_data, zoom_in_location = 300)
```

```{r message=FALSE, echo=FALSE, results='hide', warning=FALSE}
shap.plot.force_plot_bygroup(plot_data)
```

# Low-Income


```{r message=FALSE, echo=FALSE, warning=FALSE}
variables <- c("GDP_growth", "GDP_p_capita_log", "Pop_log", "P_rights", "Trade_op_log", "FDI", "Exe_respect_constitution", "Civil_liberties", "RuleOfLaw", "Year", "Party_institut_idx")
#LowIncome_data <- filter(LowIncome_data, Country != "Liberia")
LowIncome_data %>% select(variables, Country) %>% data.frame() %>% drop_na()  -> stat_data
stat_data$FDI <- stat_data$FDI
stat_data %>% group_by(Country) %>%
  select(FDI, Year) %>%
  summarise(Min = round(min(FDI),2),
            '1st Qu.' = round(quantile(FDI, 0.25),2),
            Median = round(median(FDI),2),
            Mean = round(mean(FDI),2),
            '3rd Qu.' = round(quantile(FDI, 0.75),2),
            Max = round(max(FDI),2),
            Std = round(sd(FDI),2),
            Count = n(),
            'Years (Min-Max)'= paste0(as.character(min(Year)), "-",as.character(max(Year)))) -> FDI_stats
FDI_stats %>% kable() %>% kable_styling()%>%
  save_kable("tables/table8.html",
             zoom = 2)
```

```{r message=FALSE, echo=FALSE, warning=FALSE}
FDI_stats %>%
  mutate(Country = reorder(Country, Max)) %>%
  ggplot() +
  geom_segment( aes(x=Country, xend=Country, y=Min, yend=Max), color="grey") +
  geom_point( aes(x=Country, y=Min), color=rgb(0.2,0.7,0.1,0.5), size=3 ) +
  geom_point( aes(x=Country, y=Max), color=rgb(0.7,0.2,0.1,0.5), size=3 ) +
  coord_flip()+
  theme_ipsum() +
  theme(
    legend.position = "none",
  ) +
  xlab("") +
  ylab("Share of FDI in GDP")+
  scale_y_continuous(breaks=c(seq(0, 1,0.2)))+
  theme_minimal()
```

```{r message=FALSE, echo=FALSE, warning=FALSE}
data_corr <- LowIncome_data %>% select(variables) %>% select(-Year) %>% drop_na()
nums <- unlist(lapply(data_corr, is.numeric))  
```

```{r message=FALSE, echo=FALSE, warning=FALSE}
M <- data_corr[, nums]
colnames(M) <- c("GDP growth rate", "log(GDP per capita)","log(Population)","Property rights","log(Trade openness)","FDI", "Executive respects constitution","Civil Liberties","Rule of Law","Party institutionalization index")
res <- cor(M)
p.mat <- cor.mtest(M)


png('corr_plot3.png', width = 880, height = 880)

corrplot(res, is.corr = FALSE, method="color", col=col(200),
         type="upper", 
         addCoef.col = "black", # Add coefficient of correlation
         tl.col="black", tl.srt=45, #Text label color and rotation
         # Combine with significance
         p.mat = p.mat, sig.level = c(0.01), insig = 'blank', 
         # hide correlation coefficient on the principal diagonal
         diag=FALSE 
         )

dev.off()
```

## Panel Model

### Exe_respect_constitution Clustering

```{r message=FALSE, echo=FALSE, warning=FALSE}
Data_LowIncome_clust <- LowIncome_data %>% select(c(Exe_respect_constitution)) %>% scale()

fviz_nbclust(Data_LowIncome_clust, FUNcluster=kmeans, method = "silhouette") + theme_minimal()
fviz_nbclust(Data_LowIncome_clust, FUNcluster=kmeans, method = "wss") + theme_minimal()
fviz_nbclust(Data_LowIncome_clust, FUNcluster=kmeans, method = "gap_stat") + theme_minimal()

my_vector <- vector("numeric", 10L)
for(i in 2:10) {
  clusters1<-kmeans(Data_LowIncome_clust, 3) 
  my_vector[i] <- round(calinhara(Data_LowIncome_clust,clusters1$cluster),digits=2)
}
ggplot(data_frame(my_vector), aes(x=seq(1,10,1), y=my_vector)) +
  geom_line() +
  labs(title="Optimal number of clusters",
       x="Number of clusters k", y = "Calinski-Harabasz Index") + 
  geom_vline(xintercept = 3, linetype="dotted", color = "blue") + 
  scale_x_discrete(limits=seq(1,10,1)) +
  theme_minimal()  

clusters1<-kmeans(Data_LowIncome_clust, 3) # 3 clusters final

LowIncome_data$Exe_clust<-rep(0, times=dim(LowIncome_data)[1])
LowIncome_data$Exe_clust[clusters1$cluster==1]<-1
LowIncome_data$Exe_clust[clusters1$cluster==2]<-2
LowIncome_data$Exe_clust[clusters1$cluster==3]<-3

clusters_stats <- cbind(LowIncome_data$Exe_respect_constitution[clusters1$cluster==1],
                        LowIncome_data$Exe_respect_constitution[clusters1$cluster==2],
                        LowIncome_data$Exe_respect_constitution[clusters1$cluster==3])
colnames(clusters_stats) <- c("Cluster 1", "Cluster 2", "Cluster 3")
summary(clusters_stats)
LowIncome_data$Exe_clust <- ordered(LowIncome_data$Exe_clust, c("2","3", "1"))

plot_cluster <- cbind(LowIncome_data$Exe_respect_constitution, clusters1$cluster)
colnames(plot_cluster) <- c("Exe_respect_constitution", "Cluster")

ggplot(as.data.frame(plot_cluster),  aes(Exe_respect_constitution, Cluster, color=factor(Cluster))) +
  geom_point() +
  labs(title="Clusters Plot - Low-Income Countries",
       x="Exe_respect_constitution", y = "Cluster's No.") +
  scale_y_discrete(limits=seq(1,3,1)) +
  theme_minimal() +
  theme(legend.position = "none")
table(LowIncome_data$Exe_clust)
```


```{r message=FALSE, echo=FALSE, warning=FALSE}
as.data.frame(LowIncome_data) %>% mutate(Cluster = Exe_clust) %>%
  group_by(Cluster) %>%
  summarise(Min = round(min(Exe_respect_constitution),4),
            '1st Qu.' = round(quantile(Exe_respect_constitution, 0.25),4),
            Median = round(median(Exe_respect_constitution),4),
            Mean = round(mean(Exe_respect_constitution),4),
            '3rd Qu.' = round(quantile(Exe_respect_constitution, 0.75),4),
            Max = round(max(Exe_respect_constitution),4),
            Std = round(sd(Exe_respect_constitution),4),
            Count = n()) -> Exe_stats
Exe_stats %>% kable() %>% kable_styling()%>%
  save_kable("tables/table3exe.html",
             zoom = 2)
```

### model 1

```{r message=FALSE, echo=FALSE, warning=FALSE}
formula <- log(FDI) ~ GDP_growth + GDP_p_capita_log + Pop_log + Trade_op_log + Party_institut_idx + P_rights

fixed <- plm(formula, data = LowIncome_data, index = c("Country", "Year"), model = "within")
random <- plm(formula, data = LowIncome_data, index = c("Country", "Year"), model = "random")
pooled <- plm(formula, data = LowIncome_data, index = c("Country", "Year"), model = "pooling")

x <- phtest(fixed,random)
x <- x[["p.value"]]

if (x>=0.05) {
  LowIncome_model1 <- random} else{
    LowIncome_model1 <- fixed
  }# if pvalue <= 0,05 : H0:random is ejected - we use fixed effects (Hausman 1978)
summary(LowIncome_model1)

# Fixed effects test
Test_table1_LowIncome <- tidy(pFtest(fixed, pooled))
# Hausman Test
Test_table2_LowIncome <- tidy(phtest(fixed,random))

rm(random, fixed, x, pooled)   
```

### model 2

```{r message=FALSE, echo=FALSE, warning=FALSE}
formula <- log(FDI) ~ GDP_growth + GDP_p_capita_log + Pop_log + Trade_op_log + Party_institut_idx + Exe_clust

fixed <- plm(formula, data = LowIncome_data, index = c("Country", "Year"), model = "within")
random <- plm(formula, data = LowIncome_data, index = c("Country", "Year"), model = "random")
pooled <- plm(formula, data = LowIncome_data, index = c("Country", "Year"), model = "pooling")

x <- phtest(fixed,random)
x <- x[["p.value"]]

if (x>=0.05) {
  LowIncome_model2 <- random} else{
    LowIncome_model2 <- fixed
  }# if pvalue <= 0,05 : H0:random is ejected - we use fixed effects (Hausman 1978)
summary(LowIncome_model2)

# Fixed effects test
Test_table1_LowIncome <- rbind(Test_table1_LowIncome, tidy(pFtest(fixed, pooled)))
# Hausman Test
Test_table2_LowIncome <- rbind(Test_table2_LowIncome, tidy(phtest(fixed,random)))

rm(random, fixed, x, pooled)
```

### model 3

```{r message=FALSE, echo=FALSE, warning=FALSE}
formula <- log(FDI) ~ GDP_growth + GDP_p_capita_log + Pop_log + Trade_op_log + RuleOfLaw + Party_institut_idx

fixed <- plm(formula, data = LowIncome_data, index = c("Country", "Year"), model = "within")
random <- plm(formula, data = LowIncome_data, index = c("Country", "Year"), model = "random")
pooled <- plm(formula, data = LowIncome_data, index = c("Country", "Year"), model = "pooling")

x <- phtest(fixed,random)
x <- x[["p.value"]]

if (x>=0.05) {
  LowIncome_model3 <- random} else{
    LowIncome_model3 <- fixed
  }# if pvalue <= 0,05 : H0:random is ejected - we use fixed effects (Hausman 1978)
summary(LowIncome_model3)

# Fixed effects test
Test_table1_LowIncome <- rbind(Test_table1_LowIncome, tidy(pFtest(fixed, pooled)))
# Hausman Test
Test_table2_LowIncome <- rbind(Test_table2_LowIncome, tidy(phtest(fixed,random)))

rm(random, fixed, x, pooled)
```

### model 4

```{r message=FALSE, echo=FALSE, warning=FALSE}
formula <- log(FDI) ~ GDP_growth + GDP_p_capita_log + Pop_log + Trade_op_log + Civil_liberties + Party_institut_idx

fixed <- plm(formula, data = LowIncome_data, index = c("Country", "Year"), model = "within")
random <- plm(formula, data = LowIncome_data, index = c("Country", "Year"), model = "random")
pooled <- plm(formula, data = LowIncome_data, index = c("Country", "Year"), model = "pooling")

x <- phtest(fixed,random)
x <- x[["p.value"]]

if (x>=0.05) {
  LowIncome_model4 <- random} else{
    LowIncome_model4 <- fixed
  }# if pvalue <= 0,05 : H0:random is ejected - we use fixed effects (Hausman 1978)
summary(LowIncome_model4)

# Fixed effects test
Test_table1_LowIncome <- rbind(Test_table1_LowIncome, tidy(pFtest(fixed, pooled)))
# Hausman Test
Test_table2_LowIncome <- rbind(Test_table2_LowIncome, tidy(phtest(fixed,random)))

rm(random, fixed, x, pooled)
```

### model 5

```{r message=FALSE, echo=FALSE, warning=FALSE}
formula <- log(FDI) ~ lag(log(FDI)) + lag(log(FDI), 2) + GDP_growth + GDP_p_capita_log + Pop_log + Trade_op_log + Party_institut_idx

fixed <- plm(formula, data = LowIncome_data, index = c("Country", "Year"), model = "within")
random <- plm(formula, data = LowIncome_data, index = c("Country", "Year"), model = "random")
pooled <- plm(formula, data = LowIncome_data, index = c("Country", "Year"), model = "pooling")

x <- phtest(fixed,random)
x <- x[["p.value"]]

if (x>=0.05) {
  LowIncome_model5 <- random} else{
    LowIncome_model5 <- fixed
  }# if pvalue <= 0,05 : H0:random is ejected - we use fixed effects (Hausman 1978)
summary(LowIncome_model5)

# Fixed effects test
Test_table1_LowIncome <- rbind(Test_table1_LowIncome, tidy(pFtest(fixed, pooled)))
# Hausman Test
Test_table2_LowIncome <- rbind(Test_table2_LowIncome, tidy(phtest(fixed,random)))

rm(random, fixed, x, pooled)
```

### Panel Summary

```{r message=FALSE, echo=FALSE, warning=FALSE}
tab_model(LowIncome_model1, LowIncome_model2, LowIncome_model3, LowIncome_model4, LowIncome_model5,
          dv.labels = c("Model 1", "Model 2", "Model 3", "Model 4", "Model 5"),
          pred.labels = var_labels,
          show.ci = FALSE,
          p.style = "stars")
```

## XGBoost

### Sampling

```{r message=FALSE, echo=FALSE, warning=FALSE}
sample = sample.split(LowIncome_data$num, SplitRatio = .8)
LowIncome_train = subset(LowIncome_data, sample == TRUE)
LowIncome_test  = subset(LowIncome_data, sample == FALSE)
dim(LowIncome_train)
dim(LowIncome_test)
```

### Model

```{r message=FALSE, warning=FALSE, results='hide'}
set.seed(123456789)

y_var <-  "FDI"
dataX <- as.matrix(cbind(LowIncome_data[,c(1:4,13)], as.numeric(LowIncome_data$Exe_clust)))
colnames(dataX) <- c("GDP growth rate","log(GDP per capita)","log(Population)", "log(Trade openness)","Party institutionalization index","Executive respects constitution")

param_list <- list(objective = "reg:squarederror",  # For regression
                   eta = 0.05,
                   max_depth = 6,
                   gamma = 0,
                   colsample_bytree = 0.8,
                   min_child_weight = 10,
                   subsample = 0.6
                   )

mod <- xgboost::xgboost(data = dataX, 
                        label = as.matrix(LowIncome_data[[y_var]]), 
                        params = param_list, nrounds = 100)
```



```{r message=FALSE, echo=FALSE, warning=FALSE}
RSQUARE = function(y_actual,y_predict){
  cor(y_actual,y_predict)^2
}
MAPE = function(y_actual,y_predict){
  mean(abs((y_actual-y_predict)/y_actual))*100
}

print("R-squared for train data:")
RSQUARE(LowIncome_data[[y_var]], predict(mod,dataX))
#print("R-squared for test data:")
#RSQUARE(LowIncome_test[[y_var]], predict(mod, dataXtest))
print("MAPE for train data:")
MAPE(LowIncome_data[[y_var]], predict(mod, dataX))
#print("MAPE for test data:")
#MAPE(LowIncome_test[[y_var]], predict(mod, dataXtest))
```


```{r message=FALSE, echo=FALSE, warning=FALSE}
shap_values <- shap.values(xgb_model = mod, X_train = dataX)
shap_values$mean_shap_score %>% kable() %>% kable_styling()%>%
  save_kable("tables/table9.html",
             zoom = 2)
```

```{r message=FALSE, echo=FALSE, results='hide', warning=FALSE}
shap_data <- copy(shap_values$shap_score)
shap_data[, BIAS := shap_values$BIAS0]
pred_mod <- predict(mod, dataX, ntreelimit = 10)
shap_data[, `:=`(rowSum = round(rowSums(shap_data),6), pred_mod = round(pred_mod,6))]
```

```{r message=FALSE, echo=FALSE, results='hide', warning=FALSE}
# To prepare the long-format data:
shap_long <- shap.prep(xgb_model = mod, X_train = dataX)

# **SHAP summary plot**
shap.plot.summary(shap_long)

plot_shap <- cbind(LowIncome_data$Party_institut_idx, shap_values$shap_score$`Party institutionalization index`)
colnames(plot_shap) <- c("Party institutionalization index", "Shap_score")
ggplot(as.data.frame(plot_shap),  aes(`Party institutionalization index`, Shap_score, color=`Party institutionalization index`)) +
  geom_point() +
  geom_smooth() +
  labs(x="Party institutionalization index", y = "Shap score") +
  theme_minimal()
```



```{r message=FALSE, echo=FALSE, results='hide', warning=FALSE}
plot_shap <- cbind(LowIncome_data$Exe_clust,
                   shap_values$shap_score$`Executive respects constitution`,
                   LowIncome_data$Exe_respect_constitution)
colnames(plot_shap) <- c("Exe_clust", "Shap_score", "Exe_respect_constitution")

ggplot(as.data.frame(plot_shap),  aes(Exe_respect_constitution, Shap_score, color=Exe_respect_constitution, shape=ordered(Exe_clust, c("3","2", "1")))) +
  geom_point() +
  geom_smooth() +
  labs(x="Executive respects constitution", y = "Shap score",color="Executive respects constitution", shape="Cluster") +
  theme_minimal() -> p
p3 <- ggMarginal(p, type="boxplot")
p3
```

```{r message=FALSE, echo=FALSE, results='hide', warning=FALSE}
as.data.frame(plot_shap) %>% mutate(Cluster = Exe_clust) %>%
  group_by(Cluster) %>%
  summarise(Min = round(min(Shap_score),4),
            '1st Qu.' = round(quantile(Shap_score, 0.25),4),
            Median = round(median(Shap_score),4),
            Mean = round(mean(Shap_score),4),
            '3rd Qu.' = round(quantile(Shap_score, 0.75),4),
            Max = round(max(Shap_score),4),
            Std = round(sd(Shap_score),4),
            Count = n()) -> Shap_score_stats
Shap_score_stats %>% kable() %>% kable_styling()%>%
  save_kable("tables/table10.html",
             zoom = 2)
```

```{r message=FALSE, echo=FALSE, results='hide', warning=FALSE}
# choose to show top 4 features by setting `top_n = 6`, 
# set 4 clustering groups of observations.  
plot_data <- shap.prep.stack.data(shap_contrib = shap_values$shap_score, top_n = 6, n_groups = 4)
# you may choose to zoom in at a location, and set y-axis limit using `y_parent_limit`  
shap.plot.force_plot(plot_data, zoom_in_location = 300)
```

```{r message=FALSE, echo=FALSE, results='hide', warning=FALSE}
shap.plot.force_plot_bygroup(plot_data)
```

# Panel Diagnostics

```{r message=FALSE, echo=FALSE, warning=FALSE}
# 1. F test for individual effects
# If the p-value is < 0.05 then the fixed effects model is a better choice
Test_table1_Advanced$Model <- c("Advanced Markets 1", "Advanced Markets 2", "Advanced Markets 3", "Advanced Markets 4", "Advanced Markets 5")

Test_table1_Emerging$Model <- c("Emerging Markets 1", "Emerging Markets 2", "Emerging Markets 3", "Emerging Markets 4", "Emerging Markets 5")

Test_table1_LowIncome$Model <- c("Low-Income Markets 1", "Low-Income Markets 2", "Low-Income Markets 3", "Low-Income Markets 4", "Low-Income Markets 5")


rbind(Test_table1_Advanced,Test_table1_Emerging,Test_table1_LowIncome) %>% select(c(Model, method, statistic, p.value, alternative))  %>% kable() %>% kable_styling()%>%
  save_kable("tables/table1d.html",
             zoom = 2)
```

```{r message=FALSE, echo=FALSE, warning=FALSE}
# 2. Hausman Test
Test_table2_Advanced$Model <- c("Advanced Markets 1", "Advanced Markets 2", "Advanced Markets 3", "Advanced Markets 4", "Advanced Markets 5")
Test_table2_Emerging$Model <- c("Emerging Markets 1", "Emerging Markets 2", "Emerging Markets 3", "Emerging Markets 4", "Emerging Markets 5")
Test_table2_LowIncome$Model <- c("Low-Income Markets 1", "Low-Income Markets 2", "Low-Income Markets 3", "Low-Income Markets 4", "Low-Income Markets 5")

rbind(Test_table2_Advanced,Test_table2_Emerging,Test_table2_LowIncome) %>% select(c(Model, method, statistic, p.value, alternative)) %>% kable() %>% kable_styling()%>%
  save_kable("tables/table2d.html",
             zoom = 2)
```

```{r message=FALSE, echo=FALSE, warning=FALSE}
# 3. Breusch-Godfrey/Wooldridge test for serial correlation in panel models
# Advanced
Test_table3_Advanced <- tidy(pbgtest(Advanced_model1))
Test_table3_Advanced <- rbind(Test_table3_Advanced, tidy(pbgtest(Advanced_model2)))
Test_table3_Advanced <- rbind(Test_table3_Advanced, tidy(pbgtest(Advanced_model3)))
Test_table3_Advanced <- rbind(Test_table3_Advanced, tidy(pbgtest(Advanced_model4)))
Test_table3_Advanced <- rbind(Test_table3_Advanced, tidy(pbgtest(Advanced_model5)))
Test_table3_Advanced$Model <- c("Advanced Markets 1", "Advanced Markets 2", "Advanced Markets 3", "Advanced Markets 4", "Advanced Markets 5")

# Emerging
Test_table3_Emerging <- tidy(pbgtest(Emerging_model1))
Test_table3_Emerging <- rbind(Test_table3_Emerging, tidy(pbgtest(Emerging_model2)))
Test_table3_Emerging <- rbind(Test_table3_Emerging, tidy(pbgtest(Emerging_model3)))
Test_table3_Emerging <- rbind(Test_table3_Emerging, tidy(pbgtest(Emerging_model4)))
Test_table3_Emerging <- rbind(Test_table3_Emerging, tidy(pbgtest(Emerging_model5)))
Test_table3_Emerging$Model <- c("Emerging Markets 1", "Emerging Markets 2", "Emerging Markets 3", "Emerging Markets 4", "Emerging Markets 5")

# Low-income
Test_table3_Lowincome <- tidy(pbgtest(LowIncome_model1))
Test_table3_Lowincome <- rbind(Test_table3_Lowincome, tidy(pbgtest(LowIncome_model2)))
Test_table3_Lowincome <- rbind(Test_table3_Lowincome, tidy(pbgtest(LowIncome_model3)))
Test_table3_Lowincome <- rbind(Test_table3_Lowincome, tidy(pbgtest(LowIncome_model4)))
Test_table3_Lowincome <- rbind(Test_table3_Lowincome, tidy(pbgtest(LowIncome_model5)))
Test_table3_Lowincome$Model <- c("Low-Income Markets 1", "Low-Income Markets 2", "Low-Income Markets 3", "Low-Income Markets 4", "Low-Income Markets 5")
rbind(Test_table3_Advanced,Test_table3_Emerging,Test_table3_Lowincome) %>% select(c(Model,method, statistic, p.value, alternative)) %>% kable() %>% kable_styling()%>%
  save_kable("tables/table3d.html",
             zoom = 2)
```

```{r message=FALSE, echo=FALSE, warning=FALSE}
# 4. studentized Breusch-Pagan test
# H0: homoscedasticity
# H1: heteroscedasticity
# Advanced
Test_table4_Advanced <- tidy(bptest(Advanced_model1))
Test_table4_Advanced <- rbind(Test_table4_Advanced, tidy(bptest(Advanced_model2)))
Test_table4_Advanced <- rbind(Test_table4_Advanced, tidy(bptest(Advanced_model3)))
Test_table4_Advanced <- rbind(Test_table4_Advanced, tidy(bptest(Advanced_model4)))
Test_table4_Advanced <- rbind(Test_table4_Advanced, tidy(bptest(Advanced_model5)))
Test_table4_Advanced$Model <- c("Advanced Markets 1", "Advanced Markets 2", "Advanced Markets 4", "Advanced Markets 4", "Advanced Markets 5")
Test_table4_Advanced$alternative <- rep("heteroscedasticity",5)
# Emerging
Test_table4_Emerging <- tidy(bptest(Emerging_model1))
Test_table4_Emerging <- rbind(Test_table4_Emerging, tidy(bptest(Emerging_model2)))
Test_table4_Emerging <- rbind(Test_table4_Emerging, tidy(bptest(Emerging_model3)))
Test_table4_Emerging <- rbind(Test_table4_Emerging, tidy(bptest(Emerging_model4)))
Test_table4_Emerging <- rbind(Test_table4_Emerging, tidy(bptest(Emerging_model5)))
Test_table4_Emerging$Model <- c("Emerging Markets 1", "Emerging Markets 2", "Emerging Markets 4", "Emerging Markets 4", "Emerging Markets 5")
Test_table4_Emerging$alternative <- rep("heteroscedasticity",5)
# Low-income
Test_table4_Lowincome <- tidy(bptest(LowIncome_model1))
Test_table4_Lowincome <- rbind(Test_table4_Lowincome, tidy(bptest(LowIncome_model2)))
Test_table4_Lowincome <- rbind(Test_table4_Lowincome, tidy(bptest(LowIncome_model3)))
Test_table4_Lowincome <- rbind(Test_table4_Lowincome, tidy(bptest(LowIncome_model4)))
Test_table4_Lowincome <- rbind(Test_table4_Lowincome, tidy(bptest(LowIncome_model5)))
Test_table4_Lowincome$Model <- c("Low-Income Markets 1", "Low-Income Markets 2", "Low-Income Markets 4", "Low-Income Markets 4", "Low-Income Markets 5")
Test_table4_Lowincome$alternative <- rep("heteroscedasticity",5)
rbind(Test_table4_Advanced,Test_table4_Emerging,Test_table4_Lowincome) %>% select(c(Model,method, statistic, p.value,alternative)) %>% kable() %>% kable_styling()%>%
  save_kable("tables/table4d.html",
             zoom = 2)
```

```{r message=FALSE, echo=FALSE, warning=FALSE}
# 5. Balance test
#It gives the measures γ and ν from Ahrens and Pincus (1981) where for both 1 represents balanced data and the more unbalanced the data the lower the value.
# Advanced
Test_table5_Advanced <- tidy(punbalancedness(Advanced_model1))
Test_table5_Advanced <- cbind(Test_table5_Advanced, tidy(punbalancedness(Advanced_model2))[,2])
Test_table5_Advanced <- cbind(Test_table5_Advanced, tidy(punbalancedness(Advanced_model3))[,2])
Test_table5_Advanced <- cbind(Test_table5_Advanced, tidy(punbalancedness(Advanced_model4))[,2])
Test_table5_Advanced <- cbind(Test_table5_Advanced, tidy(punbalancedness(Advanced_model5))[,2])
colnames(Test_table5_Advanced) <- c("Par", "Advanced Markets 1", "Advanced Markets 2", "Advanced Markets 3", "Advanced Markets 4", "Advanced Markets 5")
Test_table5_Advanced %>% kable() %>% kable_styling()%>%
  save_kable("tables/table5d1.html",
             zoom = 2)
# Emerging
Test_table5_Emerging <- tidy(punbalancedness(Emerging_model1))
Test_table5_Emerging <- cbind(Test_table5_Emerging, tidy(punbalancedness(Emerging_model2))[,2])
Test_table5_Emerging <- cbind(Test_table5_Emerging, tidy(punbalancedness(Emerging_model3))[,2])
Test_table5_Emerging <- cbind(Test_table5_Emerging, tidy(punbalancedness(Emerging_model4))[,2])
Test_table5_Emerging <- cbind(Test_table5_Emerging, tidy(punbalancedness(Emerging_model5))[,2])
colnames(Test_table5_Emerging) <- c("Par", "Emerging Markets 1", "Emerging Markets 2", "Emerging Markets 3", "Emerging Markets 4", "Emerging Markets 5")
Test_table5_Emerging %>% kable() %>% kable_styling()%>%
  save_kable("tables/table5d2.html",
             zoom = 2)
# Low-income
Test_table5_Lowincome <- tidy(punbalancedness(LowIncome_model1))
Test_table5_Lowincome <- cbind(Test_table5_Lowincome, tidy(punbalancedness(LowIncome_model2))[,2])
Test_table5_Lowincome <- cbind(Test_table5_Lowincome, tidy(punbalancedness(LowIncome_model3))[,2])
Test_table5_Lowincome <- cbind(Test_table5_Lowincome, tidy(punbalancedness(LowIncome_model4))[,2])
Test_table5_Lowincome <- cbind(Test_table5_Lowincome, tidy(punbalancedness(LowIncome_model5))[,2])
colnames(Test_table5_Lowincome) <- c("Par", "Low-Income Markets 1", "Low-Income Markets 2", "Low-Income Markets 3", "Low-Income Markets 4", "Low-Income Markets 5")
Test_table5_Lowincome %>% kable() %>% kable_styling()%>%
  save_kable("tables/table5d3.html",
             zoom = 2)
```

```{r message=FALSE, echo=FALSE, warning=FALSE}
# 6. Tests for cross-sectional dependence
#According to Baltagi, cross-sectional dependence is a problem in macro panels with long time series. This is not much of a problem in micro panels (few years and large number of cases).
#The null hypothesis in the B-P/LM and Pasaran CD tests of independence is that residuals across entities are not correlated. B-P/LM and Pasaran CD (cross-sectional dependence) tests are used to test whether the residuals are correlated across entities*. Cross-sectional dependence can lead to bias in tests results (also called contemporaneous correlation).
# Advanced
Test_table6_Advanced <- tidy(pcdtest(Advanced_model1, test = c("lm")))
Test_table6_Advanced <- rbind(Test_table6_Advanced, tidy(pcdtest(Advanced_model2, test = c("lm"))))
Test_table6_Advanced <- rbind(Test_table6_Advanced, tidy(pcdtest(Advanced_model3, test = c("lm"))))
Test_table6_Advanced <- rbind(Test_table6_Advanced, tidy(pcdtest(Advanced_model4, test = c("lm"))))
Test_table6_Advanced <- rbind(Test_table6_Advanced, tidy(pcdtest(Advanced_model5, test = c("lm"))))
Test_table6_Advanced$Model <- c("Advanced Markets 1", "Advanced Markets 2", "Advanced Markets 3", "Advanced Markets 4", "Advanced Markets 5")

# Emerging
Test_table6_Emerging <- tidy(pcdtest(Emerging_model1, test = c("lm")))
Test_table6_Emerging <- rbind(Test_table6_Emerging, tidy(pcdtest(Emerging_model2, test = c("lm"))))
Test_table6_Emerging <- rbind(Test_table6_Emerging, tidy(pcdtest(Emerging_model3, test = c("lm"))))
Test_table6_Emerging <- rbind(Test_table6_Emerging, tidy(pcdtest(Emerging_model4, test = c("lm"))))
Test_table6_Emerging <- rbind(Test_table6_Emerging, tidy(pcdtest(Emerging_model5, test = c("lm"))))
Test_table6_Emerging$Model <- c("Emerging Markets 1", "Emerging Markets 2", "Emerging Markets 3", "Emerging Markets 4", "Emerging Markets 5")

# Low-income
Test_table6_Lowincome <- tidy(pcdtest(LowIncome_model1, test = c("lm")))
Test_table6_Lowincome <- rbind(Test_table6_Lowincome, tidy(pcdtest(LowIncome_model2, test = c("lm"))))
Test_table6_Lowincome <- rbind(Test_table6_Lowincome, tidy(pcdtest(LowIncome_model3, test = c("lm"))))
Test_table6_Lowincome <- rbind(Test_table6_Lowincome, tidy(pcdtest(LowIncome_model4, test = c("lm"))))
Test_table6_Lowincome <- rbind(Test_table6_Lowincome, tidy(pcdtest(LowIncome_model5, test = c("lm"))))
Test_table6_Lowincome$Model <- c("Low-Income Markets 1", "Low-Income Markets 2", "Low-Income Markets 3", "Low-Income Markets 4", "Low-Income Markets 5")
rbind(Test_table6_Advanced,Test_table6_Emerging,Test_table6_Lowincome) %>% select(c(Model,method, statistic, p.value, alternative)) %>% kable() %>% kable_styling()%>%
  save_kable("tables/table6d.html",
             zoom = 2)
```

```{r message=FALSE, echo=FALSE, warning=FALSE}
Test_table7_Advanced <- tidy(pcdtest(Advanced_model1, test = c("cd")))
Test_table7_Advanced <- rbind(Test_table7_Advanced, tidy(pcdtest(Advanced_model2, test = c("cd"))))
Test_table7_Advanced <- rbind(Test_table7_Advanced, tidy(pcdtest(Advanced_model3, test = c("cd"))))
Test_table7_Advanced <- rbind(Test_table7_Advanced, tidy(pcdtest(Advanced_model4, test = c("cd"))))
Test_table7_Advanced <- rbind(Test_table7_Advanced, tidy(pcdtest(Advanced_model5, test = c("cd"))))
Test_table7_Advanced$Model <- c("Advanced Markets 1", "Advanced Markets 2", "Advanced Markets 3", "Advanced Markets 4", "Advanced Markets 5")

# Emerging
Test_table7_Emerging <- tidy(pcdtest(Emerging_model1, test = c("cd")))
Test_table7_Emerging <- rbind(Test_table7_Emerging, tidy(pcdtest(Emerging_model2, test = c("cd"))))
Test_table7_Emerging <- rbind(Test_table7_Emerging, tidy(pcdtest(Emerging_model3, test = c("cd"))))
Test_table7_Emerging <- rbind(Test_table7_Emerging, tidy(pcdtest(Emerging_model4, test = c("cd"))))
Test_table7_Emerging <- rbind(Test_table7_Emerging, tidy(pcdtest(Emerging_model5, test = c("cd"))))
Test_table7_Emerging$Model <- c("Emerging Markets 1", "Emerging Markets 2", "Emerging Markets 3", "Emerging Markets 4", "Emerging Markets 5")

# Low-income
Test_table7_Lowincome <- tidy(pcdtest(LowIncome_model1, test = c("cd")))
Test_table7_Lowincome <- rbind(Test_table7_Lowincome, tidy(pcdtest(LowIncome_model2, test = c("cd"))))
Test_table7_Lowincome <- rbind(Test_table7_Lowincome, tidy(pcdtest(LowIncome_model3, test = c("cd"))))
Test_table7_Lowincome <- rbind(Test_table7_Lowincome, tidy(pcdtest(LowIncome_model4, test = c("cd"))))
Test_table7_Lowincome <- rbind(Test_table7_Lowincome, tidy(pcdtest(LowIncome_model5, test = c("cd"))))
Test_table7_Lowincome$Model <- c("Low-Income Markets 1", "Low-Income Markets 2", "Low-Income Markets 3", "Low-Income Markets 4", "Low-Income Markets 5")
rbind(Test_table7_Advanced,Test_table7_Emerging,Test_table7_Lowincome) %>% select(c(Model,method, statistic, p.value, alternative)) %>% kable() %>% kable_styling()%>%
  save_kable("tables/table7d.html",
             zoom = 2)
```

```{r message=FALSE, echo=FALSE, warning=FALSE}
# 8. Stationarity - Augmented Dickey-Fuller Test
# Advanced
Panel.set <- plm.data(Advanced_data, index = c("Country", "Year"))
Stationarity_test <- tidy(adf.test(Panel.set$FDI, k=2))
# Emerging
Panel.set <- plm.data(Emerging_data, index = c("Country", "Year"))
Stationarity_test <- rbind(Stationarity_test, tidy(adf.test(Panel.set$FDI, k=2)))
# Low Income
Panel.set <- plm.data(LowIncome_data)
Stationarity_test <- rbind(Stationarity_test, tidy(adf.test(Panel.set$FDI, k=2)))
Stationarity_test$Data <- c("Advanced", "Emerging", "Low-Income")
Stationarity_test %>% select(c(Data, method, statistic, p.value, alternative)) %>% kable() %>% kable_styling()%>%
  save_kable("tables/table8d.html",
             zoom = 2)
```

# temp
```{r message=FALSE, echo=FALSE, results='hide', warning=FALSE}
formula <- log(FDI) ~ GDP_growth + GDP_p_capita_log + Pop_log + Trade_op_log + Party_institut_idx + P_rights
DW_test <- tidy(dwtest(formula, data = Advanced_data))
formula <- log(FDI) ~ GDP_growth + GDP_p_capita_log + Pop_log + Trade_op_log + Party_institut_idx + Exe_clust
DW_test <- rbind(DW_test, tidy(dwtest(formula, data = Advanced_data)))
formula <- log(FDI) ~ GDP_growth + GDP_p_capita_log + Pop_log + Trade_op_log + RuleOfLaw + Party_institut_idx
DW_test <- rbind(DW_test, tidy(dwtest(formula, data = Advanced_data)))
formula <- log(FDI) ~ GDP_growth + GDP_p_capita_log + Pop_log + Trade_op_log + Civil_liberties + Party_institut_idx
DW_test <- rbind(DW_test, tidy(dwtest(formula, data = Advanced_data)))
formula <- log(FDI) ~ lag(log(FDI)) + lag(log(FDI), 2) + GDP_growth + GDP_p_capita_log + Pop_log + Trade_op_log + Party_institut_idx
DW_test <- rbind(DW_test, tidy(dwtest(formula, data = Advanced_data)))
DW_test$Model <- c("Advanced Markets 1", "Advanced Markets 2", "Advanced Markets 3", "Advanced Markets 4", "Advanced Markets 5")

formula <- log(FDI) ~ GDP_growth + GDP_p_capita_log + Pop_log + Trade_op_log + Party_institut_idx + P_rights
DW_test2 <- tidy(dwtest(formula, data = Emerging_data))
formula <- log(FDI) ~ GDP_growth + GDP_p_capita_log + Pop_log + Trade_op_log + Party_institut_idx + Exe_clust
DW_test2 <- rbind(DW_test2, tidy(dwtest(formula, data = Emerging_data)))
formula <- log(FDI) ~ GDP_growth + GDP_p_capita_log + Pop_log + Trade_op_log + RuleOfLaw + Party_institut_idx
DW_test2 <- rbind(DW_test2, tidy(dwtest(formula, data = Emerging_data)))
formula <- log(FDI) ~ GDP_growth + GDP_p_capita_log + Pop_log + Trade_op_log + Civil_liberties + Party_institut_idx
DW_test2 <- rbind(DW_test2, tidy(dwtest(formula, data = Emerging_data)))
formula <- log(FDI) ~ lag(log(FDI)) + lag(log(FDI), 2) + GDP_growth + GDP_p_capita_log + Pop_log + Trade_op_log + Party_institut_idx
DW_test2 <- rbind(DW_test2, tidy(dwtest(formula, data = Emerging_data)))
DW_test2$Model <- c("Emerging Markets 1", "Emerging Markets 2", "Emerging Markets 3", "Emerging Markets 4", "Emerging Markets 5")

formula <- log(FDI) ~ GDP_growth + GDP_p_capita_log + Pop_log + Trade_op_log + Party_institut_idx + P_rights
DW_test3 <- tidy(dwtest(formula, data = LowIncome_data))
formula <- log(FDI) ~ GDP_growth + GDP_p_capita_log + Pop_log + Trade_op_log + Party_institut_idx + Exe_clust
DW_test3 <- rbind(DW_test3, tidy(dwtest(formula, data = LowIncome_data)))
formula <- log(FDI) ~ GDP_growth + GDP_p_capita_log + Pop_log + Trade_op_log + RuleOfLaw + Party_institut_idx
DW_test3 <- rbind(DW_test3, tidy(dwtest(formula, data = LowIncome_data)))
formula <- log(FDI) ~ GDP_growth + GDP_p_capita_log + Pop_log + Trade_op_log + Civil_liberties + Party_institut_idx
DW_test3 <- rbind(DW_test3, tidy(dwtest(formula, data = LowIncome_data)))
formula <- log(FDI) ~ lag(log(FDI)) + lag(log(FDI), 2) + GDP_growth + GDP_p_capita_log + Pop_log + Trade_op_log + Party_institut_idx
DW_test3 <- rbind(DW_test3, tidy(dwtest(formula, data = LowIncome_data)))
DW_test3$Model <- c("Low-Income Markets 1", "Low-Income Markets 2", "Low-Income Markets 3", "Low-Income Markets 4", "Low-Income Markets 5")

rbind(DW_test,DW_test2,DW_test3) %>% select(c(Model,method, statistic, p.value, alternative)) %>% kable() %>% kable_styling()%>%
  save_kable("tables/table11dw.html",
             zoom = 2)

# ACF test vis
acf(Advanced_data$FDI)
acf(Emerging_data$FDI)
acf(LowIncome_data$FDI)
```



```{r message=FALSE, echo=FALSE, results='hide', warning=FALSE}
# 4. Tests for individual and time effects
#ols <-lm(formula, data = LowIncome_data)
#pFtest(LowIncome_model1, ols)
# 5. Tests for cross-sectional dependence
#pcdtest(Advanced_model2, test = c("lm"))
#pcdtest(LowIncome_model1, test = c("cd"))
# 6. Stationarity
#Panel.set <- plm.data(LowIncome_data, index = c("Country", "Year"))
#adf.test(Panel.set$FDI, k=2)
```